Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-20 paper/main.tex
Update main.tex
update

\subsection{Overview of World Bank Light Every Night}
World Bank Light Every Night \cite{WorldBan13:online} is a comprehensive data repository established by the World Bank in collaboration with the National Oceanic and Atmospheric Administration (NOAA) and the University of Michigan, which contains light satellite images collected at night over the past 30 years. Two sensors have been in continuous use until now: the first is the Defense Meteorological Satellite Program (DMSP) line of business scan
System (OLS), its data collection is from 1992-2017 data. The other is the Visible Infrared Imaging Radiometer Suite (VIIRS) Day and Night Band (DNB). Its main data collection is from 2012-2020.

@@

After continuous exploration, development, updates and upgrades, the University of Michigan supports access to Cloud-optimized access to GeoTIFF format (COG) files through additional processing, and also uses the Spatio-temporal Asset Catalog (STAC) standard to edit data for sharing File, and data sharing is ready. The ever-improving standards promote the integration of data to the integrity of the shared ecosystem, which is improving access to geospatial data sets, which makes it more widely accepted by the public and can easily discover, process, and analyze geospatial data. Our project data will also use cloud-optimized GeoTIFF format (COG) and STAC standards to implement network-level applications.

\subsection{Remote sensing}
NASA's research shows that modern remote sensing technology began with the invention of the camera more than 150 years ago \cite{earthdata28:online}. The first original photo appeared in the form of a "still image", but it inspired the idea and practice of people taking pictures and looking down on the surface of the earth. This idea appeared in the 1840s. The first photo was used for topographic mapping. At the end of the First World War, the cameras installed on the aircraft provided a bird's-eye view of a considerable area and provided a large amount of terrain data for military activities. After continuous research and development, the current remote sensing technology has reached a qualitative leap.

Remote sensing technology is usually used to describe objects, without direct contact, only to identify, observe and measure. Most of the data in this project comes from the detection and measurement of radiation of different wavelengths reflected or emitted from distant objects or materials. Through these radiations, they can be identified and classified by category, substance and spatial distribution\cite{earthdata28:online}Finally determine the wavelength of the light to image.

@@

Low Earth Orbit (LEO) (picture ~\ref{LEO}) is the closest orbit to the earth for a satellite. It is only less than 400 kilometers above the surface of the earth, but it may be even higher than 2000 kilometers. Range \cite{WhatisRe36:online}. Such low-orbit operation has inherent advantages for satellites in shooting satellite maps and navigation, etc. \cite{earthdata28:online}. The current high-resolution images are basically taken by it, and such an orbit is also the orbit used by the International Space Station (ISS). This design makes it easier for astronauts to travel to and from it. The satellite in this orbit moves at a speed of about 7.8 kilometers per second; it only takes 90 minutes for a satellite to orbit the earth at this speed, which means that the International Space Station orbits the earth approximately 16 times a day, which is also useful for satellite maps and satellite positioning. Provides a better experience\cite{ESAkerne12:online}.

@@

\paragraph{Geostationary}
The orbit of a geostationary satellite (picture ~\ref{Geostationary}) can only be achieved at an altitude very close to 35,786 kilometers, and the satellite can be fixed at one longitude of the equator \cite{Synchron89:online}. Such a satellite will be a place far away from the earth to observe and collect data. At the same time, it will be able to cover an area on the earth for a long time and continuously because of its location. For example, a weather satellite will operate in such an orbit. \Cite{WhatisRe36:online}. As far as the earth is concerned, the satellite operating in this way is stationary, its trajectory is synchronized with the earth, and its rotation period is also synchronized with the earth\cite{CelesTra70:online}.

@@

The visible spectrum is the part of the electromagnetic spectrum that the human eye can see, so it is also called the visible wave. For such a wave, its wavelength is usually between 380 and 700 nanometers. The rainbow is a kind of light wave in space. There are seven colors. Because each color is different, their wavelengths are also different. The purple wavelength is the shortest. About 380 nanometers, the red wavelength is the longest, about 700 nanometers\cite{Vis73:online}.

@@

UV (ultraviolet) light refers to the region of the electromagnetic spectrum between visible light and X\ rays, with a wavelength between 400 and 10 nanometers \cite{uvlight14:online}. Among ultraviolet rays, red light has the longest wavelength, while violet light has the shortest wavelength. Therefore, the longer wavelength is called ultraviolet light, and the shorter wavelength is called ultraviolet light. Nowadays, the use of ultraviolet light can be seen everywhere, such as the invention of the currency detector, and the medical application of ultraviolet light shows its value.

@@

    \begin{itemize}
        \item Low resolution: over 60m/pixel 
        \item Medium resolution: 10 ‒ 30m/pixel 
        \item High resolution ‒ ultra-high resolution: 30cm ‒ 5m/pixel
    \end{itemize}

@@

Time resolution refers to the repetitive period or frequency at which the sensor revisits the same part of the earth's 
surface. Think of it as the time to take multiple measurements of the cross-section and then reconstruct the image. This 
time is also called the "revisit time" of the satellite. For example, the greater the stripe width of a polar-orbiting 
satellite, it is regarded as the width of the sensor's "cross-orbit" field of view during the passage of the orbit, and 
the higher the resolution time \cite{Topic43:online}.

>>>>

\subsection{Overview of World Bank Light Every Night}
World Bank Light Every Night \cite{WorldBan13:online} is an integrated data collection center and data repository established by the World Bank in cooperation with the National Oceanic and Atmospheric Administration (NOAA) and the University of Michigan. It contains light collected at night. Satellite imagery for the past 30 years. So far, two sensors have been in use: the first is called DMSP-OLS, and its data collection is from 1992 to 2017. The other is called VIIRS-DNB, and its main data collection period is 2012-2020.

@@

After continuous exploration, development, updates and upgrades, the University of Michigan supports cloud-optimized access to GeoTIFF format (COG) files through additional processing, and uses the Spatio-temporal Asset Catalog (STAC) standard to edit data for sharing. File and data sharing are ready. Continuously improving standards promote the integration of data and the integrity of the shared ecosystem, which is improving access to geospatial data sets, making them more widely accepted by the public, and making it easier to discover, process, and analyze geospatial data. Our project data will also use cloud-optimized GeoTIFF format (COG) and STAC standards to implement network-level applications.

\subsection{Remote sensing}
Research conducted by NASA shows that modern remote sensing technology was invented by the inspiration of cameras for more than 150 years\cite{earthdata28:online}. The first original photo appeared in the form of a "still image", but it inspired the idea and practice of people taking pictures and looking down on the surface of the earth. This idea appeared in the 1840s. The first photo was used for topographic mapping. At the end of the First World War, the cameras installed on the aircraft provided a bird's-eye view of a considerable area and provided a large amount of terrain data for military activities. After continuous research and development, the current remote sensing technology has reached a qualitative leap.

Remote sensing technology is usually used to describe objects, without direct contact, only to identify, observe and measure. Most of the data collected in this project are generated by the reflection or emission of objects or materials. These differences in wavelength or degree of radiation will also have different effects on the detection and measurement data. So through the collection of radiation and wavelength, analysis plus consideration of objects, types, density, and various aspects\cite{earthdata28:online}Finally determine the wavelength of the light to image.

@@

Low Earth Orbit (LEO) (picture ~\ref{LEO}) is the closest orbit to the earth for a satellite. It is only less than 400 kilometers above the surface of the earth, but it may be even higher than 2000 kilometers. Range \cite{WhatisRe36:online}. Such low-orbit operation has inherent advantages for satellites in shooting satellite maps and navigation, etc. \cite{earthdata28:online}. The current high-resolution images are basically taken by it, and such orbits are often used by the International Space Station (ISS) as a common orbit. The design of this orbit makes it easier for astronauts to travel to and from it. The satellite in this orbit moves at a speed of about 7.8 kilometers per second; for a low-orbit satellite, it usually orbits the earth at this speed for only 90 minutes, which means 16 orbits around the earth. It provides good feasibility for the realization of satellite map technology and satellite positioning technology\cite{ESAkerne12: online}.

@@

\paragraph{Geostationary}
The geostationary satellite's orbit (picture ~\ref{Geostationary}) can only be achieved at an altitude close to 35786 kilometers, and such satellites need to be detected at a fixed equatorial latitude\cite{Synchron89:online}. Such a satellite will be a place far away from the earth to observe and collect data. At the same time, it will be able to cover an area on the earth for a long time and continuously because of its location. For example, a weather satellite will operate in such an orbit. \Cite{WhatisRe36:online}. As far as the earth is concerned, the satellite operating in this way is stationary, its trajectory is synchronized with the earth, and its rotation period is also synchronized with the earth\cite{CelesTra70:online}.

@@

The visible spectrum is the part of the electromagnetic spectrum that the human eye can see, so it is also called the visible wave. For such a wave, its wavelength is usually between 380 and 700 nanometers. The rainbow is a kind of light wave in space. There are seven colors. Because each color is different, their wavelengths are also different.Violet has the shortest wavelength. About 380 nanometers, the longest red wavelength, about 700 nanometers\cite{Vis73:online}.

@@

UV light is in the electromagnetic spectrum between visible and X-rays, and its wavelength is between 400 and 10 nanometers \cite{uvlight14:online}. Among the ultraviolet light, red light has the longest wavelength, while violet light has the shortest wavelength. Therefore, the longer wavelength is called ultraviolet light, and the shorter wavelength is called ultraviolet light. Nowadays, the use of ultraviolet light can be seen everywhere, such as the invention of the currency detector, and the medical application of ultraviolet light shows its value.

@@

    \begin{itemize}
        \item Low resolution(LR): over 60m pixel 
        \item Medium resolution(MR): 10 ‒ 30m pixel 
        \item High resolution(HR) ‒ ultra-high resolution(UR): 30cm ‒ 5m pixel
    \end{itemize}

@@

Time resolution refers to the repetitive period or frequency surface of the sensor revisiting the same part of the earth. Think of it as the time to take multiple measurements of the cross section and then reconstruct the image. This time is also called the "revisit time" of the satellite.For example, the greater the stripe width of a polar-orbiting satellite, it is regarded as the width of the sensor's "cross-orbit" field of view during the passage of the orbit, and 
the higher the resolution time \cite{Topic43:online}.
